Exact asymptotic expressions for local clustering in hyperbolic random graphs

### 2018-10-24 proof_overview.tex
started on Section 4.6. Added task for Markus.
Started merging Nikolaos results into paper

We will write $p = (x, y)$ for points in $\Rcal$. Then the \emph{infinite limit model} $G_{\mathcal{P}}(\alpha, \nu)$ is defined to have vertex set $\mathcal{P}$ and edge set such that
\[
	(p_i, p_j) \in E(G_{\mathcal{P}}(\alpha, \nu)) \iff |x_i - x_j| \leq e^{\frac{y_i + y_j}{2}}.
\]
For a point $p \in \Rcal$, we will write $\BallPo{p}$ to denote the \emph{ball} around $p$, i.e.
\begin{equation}\label{eq:def_ball_P}
	\BallPo{p} = \{p^\prime \in \Rcal : |x - x^\prime| \leq e^{\frac{y + y^\prime}{2}}\}.
\end{equation}
With this notation we then have that $\BallPo{p} \cap \mathcal{P}$ denotes the set of neighbors of a vertex $p \in G_\Pcal(\alpha,\nu)$.  We denote the intensity measure of the Poisson process $\mathcal{P}$ by $\mu_{\alpha, \nu}$, i.e. for every Borel-measurable subset $S \subseteq \mathbb{R} \times \mathbb{R}_+$
\begin{equation}\label{eq:def_mu_P}
	\mu_{\alpha,\nu}(S) = \int_S f_{\alpha,\nu}(x,y) \, dx \, dy,
\end{equation}
and for any point $p \in \Rcal$ we let $\eta_p$ be the corresponding probability measure on $\BallPo{p}$ 
\begin{equation}\label{eq:def_etq_P}
	\eta_p(S) = \frac{\mu_{\alpha,\nu}(S \cap \BallPo{p})}{\mu_{\alpha,\nu}(\BallPo{p})}.
\end{equation}
In addition we use $\rho(p,k)$ and $\rho(y,k)$ (for a point $p=(x,y) \in \mathcal{R}$) to denote the probability mass function of a Poisson random variable with expectation 
\begin{equation}\label{eq:mu_y_P}
	\mu_{\alpha, \nu}(\BallPo{p}) = \int_0^\infty \int_{-\infty}^\infty \ind{|x-x^\prime| \le e^{\frac{y + y^\prime}{2}}}
	f_{\alpha,\nu}(x^\prime, y^\prime) \, dx^\prime \, dy^\prime 
	= \frac{4\alpha \nu}{(2\alpha - 1)\pi} e^{\frac{y}{2}} := \xi_{\alpha,\nu}e^{\frac{y}{2}},
\end{equation}
i.e.
\[
	\rho(p,k) = \rho(y,k) = \Prob{\Po\left(\xi_{\alpha,\nu} e^{y/2}\right) = k}.
\]
Note that $\rho(y,k)$ denote the probability that a node $(x,y) \in G_{\Pcal}(\alpha,\nu)$ has degree $k$.

>>>>

We will write $p = (x, y)$ for points in $\Rcal$. Then the \emph{infinite limit model} $G_{\mathcal{P}}(\alpha, \nu)$ is defined to have vertex set $\mathcal{P}$ and edge set such that
\[
	(p_i, p_j) \in E(G_{\mathcal{P}}(\alpha, \nu)) \iff |x_i - x_j| \leq e^{\frac{y_i + y_j}{2}}.
\]
For a point $p \in \Rcal$, we will write $\BallPo{p}$ to denote the \emph{ball} around $p$, i.e.
\begin{equation}\label{eq:def_ball_P}
	\BallPo{p} = \{p^\prime \in \Rcal : |x - x^\prime| \leq e^{\frac{y + y^\prime}{2}}\}.
\end{equation}
With this notation we then have that $\BallPo{p} \cap \mathcal{P}$ denotes the set of neighbors of a vertex $p \in G_\Pcal(\alpha,\nu)$.  We denote the intensity measure of the Poisson process $\mathcal{P}$ by $\mu_{\alpha, \nu}$, i.e. for every Borel-measurable subset $S \subseteq \mathbb{R} \times \mathbb{R}_+$
\begin{equation}\label{eq:def_mu_P}
	\mu_{\alpha,\nu}(S) = \int_S f_{\alpha,\nu}(x,y) \, dx \, dy,
\end{equation}
and for any point $p \in \Rcal$ we let $\eta_p$ be the corresponding probability measure on $\BallPo{p}$ 
\begin{equation}\label{eq:def_etq_P}
	\eta_p(S) = \frac{\mu_{\alpha,\nu}(S \cap \BallPo{p})}{\mu_{\alpha,\nu}(\BallPo{p})}.
\end{equation}

Most of the subsequent analysis in this paper will make use of the~\emph{Campbell-Mecke} formula. 
For a Poisson point process $\mathcal{P}$ on a measurable space $S$ with intensity $\lambda$ and a measurable non-negative function $h: S^r \rightarrow \mathbb{R}$ we have
\begin{equation}\label{eq:def_Campbell-Mecke}
\begin{split}
& \Exp{\sum_{x_1,\ldots, x_r \in \mathcal{P}}^{\neq} h (x_1, \ldots, x_r,
\mathcal{P} \setminus \{x_1,\ldots, x_r\}) }\\
& = \int_S \cdots \int_S
\Exp{h(x_1,\ldots, x_r,\mathcal{P} \setminus \{x_1,\ldots, x_r\}) \lambda (x_1) \cdots \lambda (x_r) dx_1 \cdots dx_r},
\end{split}
\end{equation}
where the sum ranges over all distinct $r$-tuples of points of $\mathcal{P}$.

Using the Campbell-Mecke formula we can compute the density of the ball $\BallPo{p}$ as
\begin{equation}\label{eq:mu_ball_y_P}
	\mu_{\alpha, \nu}(\BallPo{p}) = \int_0^\infty \int_{-\infty}^\infty \ind{|x-x^\prime| \le e^{\frac{y + y^\prime}{2}}}
	f_{\alpha,\nu}(x^\prime, y^\prime) \, dx^\prime \, dy^\prime 
	= \frac{4\alpha \nu}{(2\alpha - 1)\pi} e^{\frac{y}{2}} := \xi_{\alpha,\nu}e^{\frac{y}{2}},
\end{equation}

We shall use $\rho(p,k)$ and $\rho(y,k)$ (for a point $p=(x,y) \in \mathcal{R}$) to denote the probability mass function of a Poisson random variable with expectation $\mu_{\alpha, \nu}(\BallPo{p})$, i.e.
\[
	\rho(p,k) = \rho(y,k) = \Prob{\Po\left(\xi_{\alpha,\nu} e^{y/2}\right) = k}.
\]
Note that $\rho(y,k)$ denote the probability that a node $(x,y) \in G_{\Pcal}(\alpha,\nu)$ has degree $k$.
